---
title: "Segmenting Transcriptomics in Spatial Neighborhoods"
author: "Nischal Bhandari"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Segmenting Transcriptomics in Spatial Neighborhood}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Objectives
1. To find the spatially variable genes on the tissue based on spatial autocorrelation statistics (Moran's I)
2. To take the spatially variable genes and study their hotspots and immediate neighborhood

```         
output: 
  rmarkdown::html_vignette:
    css: mystyles.css
```

## Dependencies

The figure sizes have been customised so that you can easily put two images side-by-side.

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

```         
output:
  rmarkdown::html_vignette:
    fig_caption: yes
```

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes[^1], and tables, e.g. using `knitr::kable()`.

[^1]: A footnote here.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither." ([via](https://twitter.com/hadleywickham/status/504368538874703872))
